%-------------------------
% Resume in LaTeX
% Author : Areeya Mae Nacional
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center}
    \textbf{\Huge \scshape Areeya Mae Nacional} \\ \vspace{1pt}
    \href{https://areeyavera.github.io}{\underline{areeyavera.github.io}} $|$ \href{mailto:maepython@gmail.com}{\underline{maepython@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/areeya-mae-nacional-492592195/}{\underline{linkedin.com/in/areeya}} $|$
    \href{https://github.com/areeyavera}{\underline{github.com/areeyavera}}
\end{center}

%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Accenture}{Gateway Cubao}
      {Software Engineer Analyst}{Feb 2019 - Present}
      \resumeItemListStart
        \resumeItem{Handle end-to-end SAP Ariba support including S/4 HANA and CIG monitoring, with a focus on transactional data for Purchase Orders, Invoices, Service Entry Sheets, Order Requests, and Receipts.}
        \resumeItem{Perform manual reprocessing of failed transactions in CIG and resolve issues with stuck Purchase Requests in Ordering.}
        \resumeItem{Manage user data in S/4 HANA, including access updates and spend limit adjustments.}
        \resumeItem{Investigate and resolve issues related to Purchase Requests, Purchase Orders, Contracts, and Invoices; conduct defect analysis and validation.}
        \resumeItem{Support incident, change, and problem management processes across multiple client environments.}
        \resumeItem{Perform regression testing and execute test cases in Ariba's DFM and Test environments.}
        \resumeItem{Create and maintain user guides and test documentation to support smooth client onboarding and product updates.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Work Exposure}
  \resumeSubHeadingListStart
    \resumeSubheading
      {House of Representatives}{Quezon City, Philippines}
      {IT Support}{Dec 2017 - Apr 2018}
      \resumeItemListStart
        \resumeItem{Provided IT support and coordination services for the House of Representatives.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Caloocan City}{Caloocan, Philippines}
      {Bachelor of Science in Computer Science}{Mar 2015 - Dec 2019}
  \resumeSubHeadingListEnd

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
   \small{\item{
     \textbf{SAP Ariba}{: Buying \& Invoicing, Test Environment, Incident, Change \& Problem Management} \\
     \textbf{S/4 HANA CIG}{: Transactional Data Management} \\
     \textbf{Business Processes}{: Functional Analysis \& Issue Resolution, Business Network Monitoring (PO, Invoice, SES)} \\
     \textbf{Programming}{: HTML, CSS, JavaScript}
   }}
 \end{itemize}

\end{document}
